---
title: "Baysien"
format: html
editor: visual
---

## Survival Analysis

## A mathematical proof of \$S\_{A}(t) = S\_{B}(t)\^{HR}\$, the Proportional hazards assumption.

Under the Proportional hazards assumption, any ratios of hazard functions at any one time are constant.

I provide an example assuming we are comparing the efficacy of two treatment groups denoted by, \$i\$:

-   Treatment A, denoted as A, has survival curve \$S\_{A}(t)\$

-   Treatment B, denoted as B, has survival curve \$S\_{B}(t)\$

Other important notations include :

-   Hazard \*\*rate\*\* \$h\_{A}(t)\$ with dependancy to time \$t\$

-   Cumulative Hazard function \$H\_{A}(t)\$, equivalent to \$\\int h\_{A}(u) du\$

-   Hazard \*\*ratio\*\* \$HR\$

-   multiplication "\${.}\$"

The proportional hazards assumption is such that the hazard functions for any individual is a fixed proportion of hazard to any other covariate.

Since we are interested in proofing this equation (1) :

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
